Stateless Model Checking with Data-Race Preemption Points

### 2016-08-27 oopsla-16/design.tex
minor touch ups
fix some camready todo layout issues now that we are swimming in free space
buncha minor prose tweaks
change formatting according to camready author package
take care of some TODO CAMREADies
oopsla: last revisions :O

{\bf Na\"ive approach.}
Given unlimited CPU time for testing,
we would always switch to the new maximal state space whenever adding a new PP.
The maximal state space is guaranteed to subsume all execution sequences reachable in any subset state space,
so considering any incomplete subset of the known PPs would be duplicate work.
Algorithm~\ref{alg:algorithm0} demonstrates this na\"ive approach.
It would be seeded with the set of all statically-known synchronization API PPs,
and invoked whenever a new data race PP is added.
%
Our proofs in \sect{\ref{sec:totalverif}},
being concerned with the verification guarantee provided when \quicksand~completes within the CPU budget,
are based on this simple version of Iterative Deepening.
%

@@

\begin{algorithm}[t]
	\SetKwInOut{Input}{Input}
	%\textbf{Function} GetBestJob($j_0$, PendingJobs, SuspendedJobs): \\
	\Input{$j$, the currently-running job}
	%\Input{$eta$, $j_0$'s predicted completion time}
	\Input{\AllPPs, the set of all known preemption points} %, sorted by decreasing heuristic priority}
	%\Input{\SuspendedJobs, the list of already-suspended jobs, sorted by increasing ETA}
	%\Input{$T$, the remaining time in the CPU budget}
	\eIf{$\exists p \in \AllPPs . p \not\in \GetPPSet{j}$}{
		return NewJob(\AllPPs) // New maximal state space
	}{
		return $j$ // $j$ is still maximal
	}
	\caption{Na\"ive Iterative Deepening method}
	\label{alg:algorithm0}
\end{algorithm}

@@

\subsection{Initial PP configuration}
\label{sec:initial-pp}

@@

\subsection{Data-race preemption points}
\label{sec:classifying}

@@

Furthermore, we do not always strictly increase the number of PPs when we find a new data race.
For each instruction involved in a data race, \quicksand~adds two new jobs:
a ``small'' job to preempt on that instruction only (line 5),
and a ``big'' job to preempt on that instruction as well as each PP used by the reporting job (line 2).
%
Hence,
%together with the logic in \sect{\ref{sec:classifying}},
each {\em pair} of racing accesses will spawn four new jobs, as shown in Figure~\ref{fig:new-dr-jobs}.
%
The rationale of spawning multiple jobs is that we don't know in advance which will be most fruitful:
while the big job risks not completing in time,
the small job risks missing the data race entirely if the original PPs were required to expose it.
% TODO CAMREADY: Put numbers here.
In practice, we observed some bugs found quickly by these small jobs, and other bugs missed by the small jobs found eventually by the big jobs.
This phenomenon motivates Iterative Deepening to prioritize jobs at run-time.

\begin{figure}[t]
	% TODO CAMREADY: increase back to 0.48
	\hspace{1em}\includegraphics[width=0.45\textwidth]{dr-jobs-v2.pdf}
	\caption{\quicksand~manages the exploration of multiple state spaces, communicating with each MC instance to receive ETAs, data race candidates, and bug reports.
		When an access pair is reported as a data race candidate, we generate a new PP for each access, and add new jobs corresponding to different combinations of those with the existing PPs.}
	\label{fig:new-dr-jobs}
\end{figure}

@@

%When \landslide~detects a data race, it reports each of the two memory accesses involved in the race.
%Each report indicates the program counter value (PC) associated with the access, as well as some further conditions to help filter away unrelated executions of the same instruction on different data.
%(For example, many parts of a codebase might call {\tt list\_insert()}, but only one callsite does so without adequate locking.)
%Ideally, the PC would be qualified by a full backtrace, but tracing the stack is too expensive to do for each shared memory access.
%Instead, \landslide~qualifies the PC with
%(a) the current thread ID and
%% FIXME: We don't actually do this.
%(b) the most recent {\tt call} instruction.
%% (a crude approximation of a stack trace)
%% which are much cheaper, as we carry them around all the time already
%Note that we do {\em not} qualify data races by the shared memory address,
%which can change based on different interleavings of previous code
%(for example, depending on the result of {\tt malloc()}).
%% especially when malloc is involved.
%%Figure~\ref{fig:dont-filter-dr-by-address} shows example code where qualifying by memory address will miss the bug.

@@

\subsection{Choosing the best job}

@@

%
We also account for the inherent inaccuracy of ETA estimates.
Line 1 heuristically scales up the time remaining to avoid suspending jobs too aggressively
in case their ETAs are actually overestimated.
Lines 12-14 account for the
%bizarre
possibility that among two suspended jobs,
%given two jobs,
%%$j_1,j_2$,
\GetPPSet{$j_1$} $\subset$ \GetPPSet{$j_2$}
but
\GetETA{$j_1$} $>$ \GetETA{$j_2$}.
This can arise because estimates tend to get more accurate over time,
and $j_1$ perhaps ran much longer before suspending.
% In such scenarios,
We heuristically assume the smaller job's ETA is more accurate
to avoid repeatedly resuming larger jobs briefly while their ETAs only become worse
(it lets us avoid thrashing in \quicksand).

>>>>

{\bf Na\"ive approach.}
Given unlimited CPU time for testing,
we would always switch to the new maximal state space whenever adding a new PP.
The maximal state space is guaranteed to subsume all execution sequences reachable in any subset state space,
so considering any incomplete subset of the known PPs would be duplicate work.
Algorithm~\ref{alg:algorithm0} demonstrates this na\"ive approach.
It is seeded with the set of all statically-known synchronization API PPs,
and invoked whenever a new data-race candidate is found.
%
Our proofs in \sect{\ref{sec:soundness}},
being concerned with the verification guarantee provided when \quicksand~completes within the CPU budget,
are based on this simple version of Iterative Deepening.
%

@@

\begin{algorithm}[t]
	\revisionx{
	\SetKwInOut{Input}{Input}
	%\textbf{Function} GetBestJob($j_0$, PendingJobs, SuspendedJobs): \\
	\Input{$j$, the currently-running job}
	%\Input{$eta$, $j_0$'s predicted completion time}
	\Input{\AllPPs, the set of all known preemption points} %, sorted by decreasing heuristic priority}
	%\Input{\SuspendedJobs, the list of already-suspended jobs, sorted by increasing ETA}
	%\Input{$T$, the remaining time in the CPU budget}
	\eIf{$\exists p \in \AllPPs . p \not\in \GetPPSet{j}$}{
		return NewJob(\AllPPs) // New maximal state space
	}{
		return $j$ // $j$ is still maximal
	}
	\caption{Na\"ive Iterative Deepening method}
	\label{alg:algorithm0}
	}
\end{algorithm}

@@

\subsection{Initial PP Configuration}
\label{sec:initial-pp}

@@

\subsection{Data-Race Preemption Points}
\label{sec:classifying}

@@

Furthermore, we do not always strictly increase the number of PPs when we find a new data race.
For each instruction involved in a data race, \quicksand~adds two new jobs:
a ``small'' job to preempt on that instruction only (line 5),
and a ``big'' job to preempt on that instruction as well as each PP used by the reporting job (line 2).
%
Hence,
%together with the logic in \sect{\ref{sec:classifying}},
each {\em pair} of racing accesses will spawn four new jobs, as shown in Figure~\ref{fig:new-dr-jobs}.
%
The rationale of spawning multiple jobs is that we don't know in advance which will be most fruitful:
while the big job risks not completing in time,
the small job risks missing the data race entirely if the original PPs were required to expose it.
In practice, we observed some bugs found quickly by these small jobs, and other bugs missed by the small jobs found eventually by the big jobs.
This phenomenon motivates Iterative Deepening to prioritize jobs at run-time.

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{dr-jobs-v2.pdf}
	\caption{\quicksand~manages the exploration of multiple state spaces, communicating with each MC instance to receive ETAs, data race candidates, and bug reports.
		When an access pair is reported as a data race candidate, we generate a new PP for each access, and add new jobs corresponding to different combinations of those with the existing PPs.}
	\label{fig:new-dr-jobs}
\end{figure}

@@

%When \landslide~detects a data race, it reports each of the two memory accesses involved in the race.
%Each report indicates the program counter value (PC) associated with the access, as well as some further conditions to help filter away unrelated executions of the same instruction on different data.
%(For example, many parts of a codebase might call {\tt list\_insert()}, but only one callsite does so without adequate locking.)
%Ideally, the PC would be qualified by a full backtrace, but tracing the stack is too expensive to do for each shared memory access.
%Instead, \landslide~qualifies the PC with
%(a) the current thread ID and
%% Oops! We don't actually do this.
%(b) the most recent {\tt call} instruction.
%% (a crude approximation of a stack trace)
%% which are much cheaper, as we carry them around all the time already
%Note that we do {\em not} qualify data races by the shared memory address,
%which can change based on different interleavings of previous code
%(for example, depending on the result of {\tt malloc()}).
%% especially when malloc is involved.
%%Figure~\ref{fig:dont-filter-dr-by-address} shows example code where qualifying by memory address will miss the bug.

@@

\subsection{Choosing the Best Job}

@@

%
We also account for the inherent inaccuracy of ETA estimates.
Line 1 heuristically scales up the time remaining to avoid suspending jobs too aggressively
in case their ETAs are actually overestimated.
Lines 12-15 account for the
%bizarre
possibility that among two suspended jobs,
%given two jobs,
%%$j_1,j_2$,
\GetPPSet{$j_1$} $\subset$ \GetPPSet{$j_2$}
but
\GetETA{$j_1$} $>$ \GetETA{$j_2$}.
This can arise because estimates tend to get more accurate over time,
and $j_1$ perhaps ran much longer before suspending.
% In such scenarios,
We heuristically assume the smaller job's ETA is more accurate
to avoid repeatedly resuming larger jobs briefly while their ETAs only become worse
(it lets us avoid thrashing in \quicksand).

### 2016-08-27 oopsla-16/evaluation.tex
oopsla: last revisions :O

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{nondets.pdf}
	\caption{Some data-race candidates may not be identified during a single program execution.
		Using nondeterministic data races as PPs,
		% lhb: 127.77%
		% phb: 191.30%
		\quicksand~found \revisionz{128\% (Limited HB) to 191\% (Pure HB)} as many data-race bugs compared to using single-pass candidates alone.
	}
	\label{fig:dr-falsenegs}
\end{figure}
Figure~\ref{fig:dr-falsenegs} compares the types of data-race candidates necessary to expose each data-race bug in our test suite.
The first series represents the bugs found using PPs from single-pass data-race candidates,
% not entirely true, as portend could be given data-race traces from an MC,
%but they don't do it in their paper, so i feel comfortable making this claim
i.e., the state-of-the-art approach used by \cite{racefuzzer,portend}.
The second series shows all data-race bugs \quicksand~found,
which includes the former type as well as new bugs involving nondeterministic data-races.
\revisionz{QS-LHB found 69 data-race bugs in total, 15} of which could \revisionz{not} be found with single-pass data-race candidates alone.
\revisionz{QS-PHB is even more dependent on nondeterministic data-race PPs, requiring nondeterministic data-race PPs in 21 cases among its 44 total data-race bugs.}
%In total, we found 189\% as many bugs by using nondeterministic data-race candidates as PPs.

>>>>

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{nondets.pdf}
	\caption{Some data-race candidates may not be identified during a single program execution.
		Using nondeterministic data races as PPs,
		% lhb: 127.77%
		% phb: 191.30%
		\quicksand~found \revisionz{128\% (Limited HB) to 191\% (Pure HB)} as many data-race bugs compared to using single-pass candidates alone.
	}
	\label{fig:dr-falsenegs}
\end{figure}
Figure~\ref{fig:dr-falsenegs} compares the types of data-race candidates necessary to expose each data-race bug in our test suite.
The first and third series represent the bugs found using PPs from single-pass data-race candidates,
% not entirely true, as portend could be given data-race traces from an MC,
%but they don't do it in their paper, so i feel comfortable making this claim
i.e., the state-of-the-art approach used by \cite{racefuzzer,portend}.
The second and fourth series show all data-race bugs \quicksand~found,
which includes the former type as well as new bugs involving nondeterministic data-races.
\revisionz{QS-LHB found 69 data-race bugs in total, 15} of which could \revisionz{not} be found with single-pass data-race candidates alone.
\revisionz{QS-PHB is even more dependent on nondeterministic data-race PPs, requiring nondeterministic data-race PPs in 21 cases among its 44 total data-race bugs.}
%In total, we found 189\% as many bugs by using nondeterministic data-race candidates as PPs.

### 2016-08-27 oopsla-16/intro.tex
oopsla: last revisions :O

% blah blah trite opening sentence
%As parallelism becomes ever more important for achieving high performance in modern-day programs,
%so too do advanced concurrency testing techniques become important for verifying the correctness of those programs.
Concurrency bugs are notoriously hard to find and reproduce because they only appear in specific thread interleavings, which arise at random during normal program execution.
{\em Stateless model checking} \cite{verisoft} offers a method for finding such bugs,
or verifying their absence,
%by systematically executing a program along as many distinct interleavings as possible,
by forcing a program to execute each distinct interleaving,
capturing
%and controlling
this nondeterminism in a finite state space.
Unfortunately, these state spaces explode exponentially in the size of the input program.
%Reduction
Techniques such as Dynamic Partial Order Reduction \cite{dpor} and Maximal Causality Reduction \cite{mcr} expand the limits of feasible test completion,
and search ordering strategies such as Iterative Context Bounding \cite{chess-icb} \revision{encourage}~bugs to be found sooner in a given space should they exist.

However, all stateless model checkers to date are bound by a fixed set of {\em preemption points}: code locations that define the granularity at which threads interleave.
For example, \textsc{CHESS} \cite{chess} \revisionx{by default} preempts only on synchronization operations and library calls, which can miss lock-free shared memory races.
%
On the other hand, SPIN \cite{spin} %and Inspect \cite{inspect}
%are able to preempt
preempts threads before any shared memory access.
Such fine granularity would automatically check each data race for the possibility of failure, but risks timing out before the state space can be completed. %makes full state space completion intractable for even modestly-sized tests.
\revisionx{Some tools, such as CHESS and Inspect \cite{inspect} can strike a middle ground by using compiler instrumentation to statically add preemption points on memory accesses.
Nevertheless,}
choosing preemption points is a tradeoff between schedule coverage and feasibility of completion:
%but
even with state-of-the-art reduction techniques,
\revision{fixing the degree of coverage}~in advance necessarily leaves some tests unaffordably large \cite{parrot,mcr}.
%This work shows how to avoid making that tradeoff decision in advance.

>>>>

% blah blah trite opening sentence
%As parallelism becomes ever more important for achieving high performance in modern-day programs,
%so too do advanced concurrency testing techniques become important for verifying the correctness of those programs.
Concurrency bugs are notoriously hard to find and reproduce because they appear only in specific thread interleavings, which arise at random during normal program execution.
{\em Stateless model checking} \cite{verisoft} offers a method for finding such bugs,
or verifying their absence,
%by systematically executing a program along as many distinct interleavings as possible,
by forcing a program to execute each distinct interleaving,
capturing
%and controlling
this nondeterminism in a finite state space.
Unfortunately, these state spaces explode exponentially in the size of the input program.
%Reduction
Techniques such as Dynamic Partial Order Reduction \cite{dpor} and Maximal Causality Reduction \cite{mcr} expand the limits of feasible test completion,
and search ordering strategies such as Iterative Context Bounding \cite{chess-icb} \revision{encourage}~bugs to be found sooner in a given space should they exist.

However, all stateless model checkers to date are bound by a fixed set of {\em preemption points}: code locations that define the granularity at which threads interleave.
For example, \textsc{CHESS} \cite{chess} \revisionx{by default} preempts only on synchronization operations and library calls, which can miss lock-free shared memory races.
%
On the other hand, SPIN \cite{spin} %and Inspect \cite{inspect}
%are able to preempt
preempts threads before any shared memory access.
Such fine granularity would automatically check each data race for the possibility of failure, but risks timing out before the state space can be completed. %makes full state space completion intractable for even modestly-sized tests.
\revisionx{Some tools, such as CHESS and Inspect \cite{inspect}, can strike a middle ground by using compiler instrumentation to statically add preemption points on memory accesses.
Nevertheless,}
choosing preemption points is a tradeoff between schedule coverage and feasibility of completion:
%but
even with state-of-the-art reduction techniques,
\revision{fixing the degree of coverage}~in advance necessarily leaves some tests unaffordably large \cite{parrot,mcr}.
%This work shows how to avoid making that tradeoff decision in advance.

### 2016-08-27 oopsla-16/overview.tex
oopsla: last revisions :O

The checker defines the granularity of thread interleavings by the {\em preemption points} it uses to switch threads.
Most model checkers \cite{chess,dbug-ssv} choose synchronization/thread library API boundaries for these points;
in our example program, these would be lines 1, 4, and 7.
Figure~\ref{fig:id} shows several possible resulting state spaces.
The approach of prior work is to enable all preemption points simultaneously, i.e., to test only the state space denoted (d).

>>>>

The checker defines the granularity of thread interleavings by the {\em preemption points} it uses to switch threads.
Most model checkers \cite{chess,dbug-ssv} choose synchronization and thread library API boundaries for these points;
in our example program, these would be lines 1, 4, and 7.
Figure~\ref{fig:id} shows several possible resulting state spaces.
The approach of prior work is to enable all preemption points simultaneously, i.e., to test only the state space denoted (d).

### 2016-08-27 oopsla-16/soundness.tex
oopsla: last revisions :O

\begin{definition}[Reachability]
A data race candidate, and its associated PPs, are reachable if it will be identified by an MC configured to preempt only on already-reachable PPs.
\end{definition}
Initially, the statically-available synchronization API PPs are reachable. Reachability of data-race PPs is transitive.

@@

We identify a particular class of false positive data-race candidates \revisionx{under Limited HB} in which the associated memory was recycled by re-allocation between the two accesses.
Figure~\ref{fig:recycle} shows a common code pattern and interleaving which can expose such behaviour.
If the {\tt malloc} on line 4 returns the same address passed to {\tt free} on line 2, then lines 1 and 7 will be flagged as a \revision{potential}~data race.
We call this a {\em malloc-recycle data race \revision{candidiate}}.
To the human eye, this is obviously a false positive: reordering lines 4-7 before lines 1-2 will change {\tt malloc}'s return value, causing {\tt x} and {\tt y} to no longer collide.
Here, Thread 2's logic usually corresponds to an initialization pattern \cite{eraser}, but for generality we have added a {\tt publish} action on line 6.

>>>>

\begin{definition}[Reachability]
A data race candidate, and its associated PPs, are reachable if it will be identified by a MC configured to preempt only on already-reachable PPs.
\end{definition}
Initially, the statically-available synchronization API PPs are reachable. Reachability of data-race PPs is transitive.

@@

We identify a particular class of false positive data-race candidates \revisionx{under Limited HB} in which the associated memory was recycled by re-allocation between the two accesses.
Figure~\ref{fig:recycle} shows a common code pattern and interleaving which can expose such behaviour.
If the {\tt malloc} on line 4 returns the same address passed to {\tt free} on line 2, then lines 1 and 7 will be flagged as a \revision{potential}~data race.
We call this a {\em malloc-recycle data race \revision{candidiate}}.
To the human eye, this is obviously a false positive: reordering lines 4-7 before lines 1-2 will change {\tt malloc}'s return value, causing {\tt x} and {\tt y} to no longer collide.
Here, Thread 2's logic usually corresponds to an initialization pattern \cite{eraser}, but for generality we have added an arbitrary {\tt publish} action on line 6.

### 2016-08-27 oopsla-16/warpzone.tex
split the giant table by making an auxiliary table for dr statistics; add purehb/shmem to table; add discussion of pure hb
take care of some TODO CAMREADies
oopsla: last revisions :O

% TODO CAMREADY: Measure how much subset overlap there is.
{\bf Avoiding redundant work.}
When we extend a small state space with more PPs, the new state space is guaranteed to test a superset of interleavings compared to the old one.
Any interleaving which does not preempt threads on any of the new PPs will be repeated work.
%Because we prioritize completing small state spaces before extending them with more PPs,
%the superset state spaces we run later will repeat each branch of their already-completed subsets.
%
%We measured the proportion of repeated work among completed state spaces across our test suite;
%on average, {\bf \large 999\%} of the interleavings in each test were repeated, with some tests as high as {\bf \large 9999\%}.
This may make us slower than SSS-MC to find certain bugs,
for example, if both {\tt lock} and {\tt unlock} PPs together expose a bug, but not either alone.
%Similarly, when pursuing total verification (\sect{\ref{sec:totalverif}}),
%if the state space resulting from preempting on every instruction could be completed,
%an SSS-MC tool such as \cite{spin} might achieve that verification faster,
%as Iterative Deepening will test many subsets of data-race PPs first.
Predicting whether an upcoming interleaving has already been tested is not straightforward,
but we believe future implementations
%of Iterative Deepening
could incorporate cross-job memoization
to prune some or all such repeated work.
\revisionx{Prioritizing the maximal state space in particular could also improve completion times:
whenever the maximal job finishes with no new data-races, future implementations could immediately prune all subset jobs and declare a total verification.}

{\bf Finer-grained PP subsets.}
\quicksand~was able to partially guarantee safety for some PPs in 89\% of tests with too-large maximal state spaces.
However, in 4 cases, no more than the minimal state space could be verified,
and in 6 others, no state spaces were completed at all.
%Larger state spaces often result from finer-grained locking,
%which can indicate a more intricate concurrent algorithm or an unnecessarily complicated design.
%Such programs may require even more rigorous verification than a program with a single global lock.
%Hence these corner cases are important to consider for future work.
While we used {\tt within\_function} (\sect{\ref{sec:landslide}}) {\em statically} to restrict where PPs could arise in advance of the test,
%we envision
future
%Iterative Deepening
implementations could use this mechanism to {\em dynamically} subset PPs further,
making partial verification of larger tests possible.
%enabling partial verification of such large tests. % if need space
%Because our current implementation does not avoid repeated interleavings across state spaces,
%as discussed above,
%we were limited to a small number of very basic PP subsets to statically seed the exploration

@@

Likewise, when full verification is not computationally feasible,
some jobs with data-race PPs will time out.
We cannot guarantee those races are
%false positives or
benign, even though no bug was found.
In the ``Untested DR PPs'' column of Table~\ref{tab:drbugs}, we show how many such candidates we could not verify (32\%).
For a more formal treatment of these cases, we refer the reader to the {\em k-witness harmless} metric introduced by \cite{portend},
which could be combined with \quicksand~in future work.
% Future work: Add parallel DPOR so you can fill your spare CPUs when there are fewer than the max number of jobs.

>>>>

% Measure how much subset overlap there is.
% Sorry past-me, mot going to do this.
{\bf Avoiding redundant work.}
When we extend a small state space with more PPs, the new state space is guaranteed to test a superset of interleavings compared to the old one.
Any interleaving which does not preempt threads on any of the new PPs will be repeated work.
%Because we prioritize completing small state spaces before extending them with more PPs,
%the superset state spaces we run later will repeat each branch of their already-completed subsets.
%
%We measured the proportion of repeated work among completed state spaces across our test suite;
%on average, {\bf \large 999\%} of the interleavings in each test were repeated, with some tests as high as {\bf \large 9999\%}.
This may make us slower than SSS-MC to find certain bugs,
for example, if both {\tt lock} and {\tt unlock} PPs together expose a bug, but not either alone.
%Similarly, when pursuing total verification (\sect{\ref{sec:totalverif}}),
%if the state space resulting from preempting on every instruction could be completed,
%an SSS-MC tool such as \cite{spin} might achieve that verification faster,
%as Iterative Deepening will test many subsets of data-race PPs first.
Predicting whether an upcoming interleaving has already been tested is not straightforward,
but we believe future implementations
%of Iterative Deepening
could incorporate cross-job memoization
to prune some or all such repeated work.
\revisionx{Prioritizing the maximal state space in particular could also improve completion times:
whenever the maximal job finishes with no new data-races, future implementations could immediately prune all subset jobs and declare a total verification.}

{\bf Finer-grained PP subsets.}
\quicksand~was able to partially guarantee safety for some PPs in \revisionz{93\%} of tests with too-large maximal state spaces.
However, in \revisionz{6} cases, no more than the minimal state space could be verified,
and in \revisionz{18} others, no state spaces were completed at all.
%Larger state spaces often result from finer-grained locking,
%which can indicate a more intricate concurrent algorithm or an unnecessarily complicated design.
%Such programs may require even more rigorous verification than a program with a single global lock.
%Hence these corner cases are important to consider for future work.
While we used {\tt within\_function} (\sect{\ref{sec:landslide}}) {\em statically} to restrict where PPs could arise in advance of the test,
%we envision
future
%Iterative Deepening
implementations could use this mechanism to {\em dynamically} subset PPs further,
making partial verification of larger tests possible.
%enabling partial verification of such large tests. % if need space
%Because our current implementation does not avoid repeated interleavings across state spaces,
%as discussed above,
%we were limited to a small number of very basic PP subsets to statically seed the exploration

@@

Likewise, when full verification is not computationally feasible,
some jobs with data-race PPs will time out.
We cannot guarantee those races are
%false positives or
benign, even though no bug was found.
In the ``Untested DR PPs'' column of Table~\ref{tab:drstatistix}, we show how many such candidates we could not verify (\revisionz{38\%}).
For a more formal treatment of these cases, we refer the reader to the {\em k-witness harmless} metric introduced by \cite{portend},
which could be combined with \quicksand~in future work.
% Future work: Add parallel DPOR so you can fill your spare CPUs when there are fewer than the max number of jobs.
